Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Fixes typo
Removes less necessary part of l-bits section

\paragraph*{A special case}

We will start with a special case of the \(l\)-bit problem.
For a session~\(i\), we have two possible responses to the two challenges:
\(s_i = r_i + c\alpha\) and \(s_i' = r_i + c'\alpha\).
Let \(c = 1\) and \(c' = 0\).
We assume that the adversary learns all \(m\) bits of \(s_i\), but only \(l\) 
bits of \(s_i'\).
This special case yields the linear equation system
\begin{align*}
  s_i &= r_i + \alpha
  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha &\pmod q\\
  s_i'[j_1] &= b_{j_1} &\pmod 2\\
  s_i'[j_2] &= b_{j_2} &\pmod 2\\
            &\vdots \\
  s_i'[j_l] &= b_{j_l}, &\pmod 2
\end{align*}
where \(s_i'[j]\) denotes the \(j\)th bit of \(s_i'\), and \(j_1, \dotsc, 
j_l\in \{0, \dotsc, m-1\}\) are indices for the bits chosen by the adversary 
and \(b_{j_1}, \dotsc, b_{j_l}\in \bin\) are the bit values.

\begin{lemma}
  Assume the special case given above.
  If \(l < m+\frac{1}{n}-1\), then the equation system is underdetermined and 
  we cannot solve for \(\alpha\).
\end{lemma}
\begin{proof}
  The equation system above yields \(l+1\) equations and \(m+1\) variables.
  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
  This yields an equation system of \(n(l+1)\) equations and \(nm+1\) variables 
  (\(\alpha\) is not repeated).
  If \(n(l+1) < nm+1\), this system is underdetermined and cannot be solved.
  After some rewriting we find that
  \begin{align*}
    n(l+1) &< nm+1 \\
    l+1 &< m + \frac{1}{n} \\
    l &< m + \frac{1}{n} -1.
  \end{align*}
  Which concludes the proof.
\end{proof}

The number of possible solutions is vital for us, since that is an estimate of 
how difficult it is for the adversary to guess \(\alpha\).

\begin{lemma}\label{simple-l-bit-advantage}
  Assume the special case above.
  There are \(m-l\) free variables, each taking a value from \(\bin\).
  This yields \(2^{m-l}-1\) unique solutions for each session.
\end{lemma}
\begin{proof}
  The result directly follows from the fact that there are \(m-l\) free 
  variables.
  Each free variable can only take two possible values (0 or 1), consequently 
  there are \(2^{m-l}-1\) unique solutions.
\end{proof}

\paragraph*{Arbitrarily chosen \(c\neq c'\)}

For any choice of \(c\) and \(c'\) such that \(c\neq c'\), we have
\begin{align}
  \label{eqn:general-c}
  s_i &= r_i + c\alpha &\pmod q\\
  \label{eqn:general-cprime}
  s_i' &= r_i + c'\alpha. &\pmod q
\end{align}
We can transform this system of equations into our special case above by 
Gaussian elimination: add \cref{eqn:general-c} multiplied by \(\frac{c'}{c}\) 
to \cref{eqn:general-cprime}.
The multiplicative inverse \(\frac{1}{c}\) exists since \(q\) is prime.
This proves the following lemma.

\begin{lemma}
  Any choice of \(c, c'\) can be turned into our special case of \(c = 1, c' = 
  0\).
\end{lemma}

This means that \cref{simple-l-bit-advantage} is also true for the general case.

@@

The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
This means that
\begin{align*}
  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
\end{align*}
We will now show how the hardenss of finding \(s'_{\text{unknown}}\) relates to 
the hardness of finding discrete logarithms.

>>>>

@@

The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
This means that
\begin{align*}
  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
\end{align*}
We will now show how the hardness of finding \(s'_{\text{unknown}}\) relates to 
the hardness of finding discrete logarithms.
